From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-08-13 WOLFHPC15/article/article.tex
section 4 helene 30_07
Adding \fix
\cf \ie
evaluation helene 30_07
Fix section & subsection title
Removed related work in sec.2
todo
wolfhpc fix language figures helene 06_08
evaluations helene 06_08
Ack++
conclusion helene 08_08
fix accents et taille references helene 08_08
evaluation introduction helene 13_08
v1 abstract helene 13_08

\documentclass{acm_proc_article-sp}
\usepackage{tikz}
\usepackage{listings}
\usepackage{url}
\usepackage{cite}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{xspace}
%----------TIKZ
\usetikzlibrary{calc,arrows,shapes,automata,petri,positioning,decorations.markings,shadows}

@@

\newcommand{\llc}{L\textsuperscript{2}C\xspace}

@@

\numberofauthors{3} 
\author{
% 1st. author
\alignauthor
Julien Bigot\\
       \affaddr{CEA, Maison de la Simulation}\\
       \affaddr{USR 3441}\\
       \affaddr{91191 Gif-sur-Yvette, France}\\ % remove cedex
       \email{julien.bigot@cea.fr}
% 1st. author
\alignauthor
Helene Coullon\\
       \affaddr{INRIA}\\
       \affaddr{ENS Lyon, 46 Allee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{helene.coullon@inria.fr}
% 2nd. author
\and
\alignauthor
Christian Perez\\
       \affaddr{INRIA}\\
       \affaddr{ENS Lyon, 46 Allee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{christian.perez@inria.fr}
}

@@

%----------------------------------------
\begin{abstract}

\end{abstract}
%----------------------------------------

@@

%----------------------------------------
\section{Introduction}
\label{sect:intro}
\input{introduction.tex}
%----------------------------------------
\section{Stencil and multi-stencil}
\label{sect:concept}
\input{concept.tex}
%----------------------------------------
\section{Overview}
\label{sect:mscac}
\input{mscac.tex}
%----------------------------------------
\section{MS Language and MSC compiler}
\label{sect:msmsc}
\input{ms_msc.tex}
%----------------------------------------
\section{Dump to a component assembly}
\label{sect:component}
\input{component.tex}
%----------------------------------------
\section{Evaluation}
\label{sect:eval}
\input{evaluation.tex}
%----------------------------------------
\section{Related Work}
\label{sect:related}
\input{related.tex}
%----------------------------------------
\section{Conclusion}
\label{sect:conclusion}
\input{conclusion.tex}
%----------------------------------------

\bibliographystyle{abbrv}
\bibliography{biblio}

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{tikz}
\usepackage{listings}
\usepackage{url}
\usepackage{cite}
\usepackage{subfig}
\usepackage{filecontents}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{todonotes}

%----------TIKZ
\usetikzlibrary{calc,arrows,shapes,automata,petri,positioning,decorations.markings,shadows}

@@

\newcommand{\fix}[1]{\todo[inline,color=red!80]{#1}}
% \renewcommand{\todo}[2][]{}

\newcommand{\cf}{\emph{cf.}\xspace}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\llc}{L\textsuperscript{2}C\xspace}

@@

\numberofauthors{3} 
\author{
% 1st. author
\alignauthor
Julien Bigot\\
       \affaddr{CEA, Maison de la Simulation}\\
       \affaddr{USR 3441, CEA Saclay}\\
       \affaddr{91191 Gif-sur-Yvette, France}\\ % remove cedex
       \email{julien.bigot@cea.fr}
% 1st. author
\alignauthor
H\'el\`ene Coullon\\
       \affaddr{INRIA}\\
       \affaddr{ENS Lyon, 46 All\'ee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{helene.coullon@inria.fr}
% 2nd. author
\and
\alignauthor
Christian P\'erez\\
       \affaddr{INRIA}\\
       \affaddr{ENS Lyon, 46 All\'ee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{christian.perez@inria.fr}
}

@@

%----------------------------------------
\begin{abstract}
High performance heterogeneous architectures continuously evolve to be more powerfull. Such architectures also usually become more difficult to use efficiently. As a scientist is not a low level and high performance programming expert, Domain Specific Languages (DSLs) are a promising solution to automatically and efficiently write high performance codes. However, if DSLs ease programming for scientists, it seems that non-maintainability and non-portability problems are deported from the scientist to the DSL designer. In this paper is presented a new approach to improve maintainability and programming productivity of DSLs through the generation of a component-based parallel runtime. To study this approach the paper presents a proper new DSL for \emph{multi-stencil} programs, which is evaluated on the real-case shallow water equations.
\end{abstract}
%----------------------------------------

@@

%----------------------------------------
\section{Introduction}
\label{sect:intro}
\input{introduction.tex}
%----------------------------------------
\section{Stencil and Multi-Stencil}
\label{sect:concept}
\input{concept.tex}
%----------------------------------------
\section{MSL and MSCAC Overview }
\label{sect:mscac}
\input{mscac.tex}
%----------------------------------------
\section{Language and Parallelization Description}
\label{sect:msmsc}
\input{ms_msc.tex}
%----------------------------------------
\section{A Component based Back-End}
\label{sect:component}
\input{component.tex}
%----------------------------------------
\section{Real-case Evaluation}
\label{sect:eval}
\input{evaluation.tex}
%----------------------------------------
\section{Related Work}
\label{sect:related}
\input{related.tex}
%----------------------------------------
\section{Conclusion}
\label{sect:conclusion}
\input{conclusion.tex}
%----------------------------------------

\section{Acknowledgments}

We acknowledge Grid'5000 for evaluations.

\small
\bibliographystyle{abbrv}
\bibliography{biblio}
